\documentclass[style=article,draft]{dlrpaper}


\title{The dlrpaper class and hacks for popular paper styles}
\author{Andreas Kl\"ockner}

\begin{document}
\maketitle

\section{Beginner's guide}
This folder contains the dlrpaper.cls documentclass and hacks for popular paper styles, such as
\begin{itemize}
	\item AIAA technical conferences: aiaa-tc.cls
	\item AIAA journals: AIAA.cls
	\item Lecture notes in Informatics: lni.cls
\end{itemize}

The hacks fix obvious bugs in the paper styles. They do not take additional options. They should be loaded as
\begin{verbatim}
	\documentclass{<original name>-hacks}
\end{verbatim}

Additionally the dlrpaper.cls class provides access to these hacks, if existent. Otherwise the original documentclass will be loaded:
\begin{verbatim}
	\documentclass[style=<original name>]{dlrpaper}
\end{verbatim}

Additional paper classes provided in this folder are:
\begin{itemize}
	\item Modelica conferences: modelica.cls
\end{itemize}

\section{Additional options to dlrpaper.cls}
\subsection{level=\textless classification level\textgreater}
If the level option is passed to the dlrpaper.cls class, the classified.sty package is loaded and a suitable classification remark of class "publication"\space is added to the document. Please see the documentation of the classified.sty for a list of available levels. The dlrpaper package additionally puts a DLR logo in the background of your draft, if the level option is used.

\subsection{draft = true / false}
The option draft = true is equivalent to the option level = draft. Additionally, the draft option is passed to the original document class.

\subsection{listofversions = \{options\}}
Loads the list of versions package with the given options. Also inserts a final section* with the listofversions.

\subsection{upload = true/false}
Suppresses the listofversions and the watermarks for uploading the document to the publisher. Also any other modification to the appearance of the paper is suppressed.

\subsection{elib = \{publisher\}}
Loads the elib documentclass as superclass with the given publisher.

\subsection{pagestyle = ...}
Sets the page style of the paper to the one provided. This can be useful to e.g.\ set pagestyle=plain in draft version, so you can reference pages with the reviewers. This option is ignored with the upload=true option.

\subsection{Other options}
All other options are passed to the original document class.

\end{document}
