\documentclass{article}

\usepackage{xcolor}
\usepackage{listings}
\lstset{language=TeX, 
        %keepspaces=false,
        breaklines=false,
        commentstyle=\color{gray},
        identifierstyle=\color{blue}}

\title{The elib class}
\author{Andreas Kl\"ockner}

\begin{document}
\maketitle
\makeatletter

\section{Introduction}
The elib document class can be used to insert copyright and citation notices into document published on the DLR elib repository. To generate a suitable cover page, just use \lstinline!\documentclass[options]{elib}!. You will need to have an empty document via \lstinline!\begin{document}\end{document}!, because the cover page is created \lstinline!\AtBeginDocument!.

\section{Copyright notice option \lstinline!publisher=<...>!}
Please select the publisher/agreement or have signed when sumbitting your paper. Then the appropriate copyright notice in inserted in the cover page. Currently there are the following defined publishers:
\begin{description}
	\item[aiaa@A] The AIAA conferences agreement A. You are not allowed to distribute such papers.
	\item[aiaa@B] The AIAA conferences agreement B. You are not allowed to do whatever you want.
	\item[ieee]   The IEEE conferences agreement. You are allowed to publish pre-prints with a prominent display of copyright, a citation and a link to IEEE XPlore.
	\item[lni]    The LNI agreement. You are allowed to archive the document on your personal website with a prominent copright and a citation.
\end{description}

Please add additional publishers to the class, by copying and extending the template \lstinline!\elib@publisher@mypublisher!.

\section{Citation notice file \lstinline!elib.bib!}
If you put a file \lstinline!elib.bib! anywhere on the \LaTeX~search path, it will be inserted in the coverpage as a full citation and in source code. You can use the DIO field to create suitable links to e.g. IEEE XPlore.

\section{PDF inclusion option \lstinline!includepdf=mydoc.pdf!}
If issued, this option includes the PDF provided in order to directly attach the cover page to your paper. This is useful, if you are allowed to publish post-prints. You can as well use Acrobat to join the files manually. This will also preserver any links in the document...

\section{TEX inclusion option \lstinline!includetex=mydoc.tex!}
If issued, this option includes the tex provided in order to directly attach the cover page to your paper. This is useful, if you are allowed to only publish pre-prints. If you use this option, the class also tries to guess your publisher based on the document class used in the original mydoc.tex.

\section{External programs}
This class issues a call to bibtex by using the external-base package. Please see the documentation of this package, too.

\end{document}